15-744 Project Proposal

### 2011-09-26 proposal/proposal.tex
Some tweaks to proposal draft.

A lightweight method is to use \t{epoll} or \t{kquery}.
This requires the application programmer to manually maintain a state machine
with

Requires a lot of complex but straightforward code which is difficult to debug.
Unsurprisingly, there exist many thin C/C++ wrappers, but these still require
...

@@

>>>>

A lightweight method is to use nonblocking IO and a multiplexing
facility such as \t{select}, \t{poll}, \t{epoll} or \t{kquery}.  This
requires the application programmer to structure the code as a state
machine, which is tedious, time-consuming, and error-prone. 
Unsurprisingly, there exist many thin
C/C++ wrappers, but these still require ...

@@

generates an explicit state-machine representation of the application logic
